Pillar 1 - Student Topic Profile

### 2019-03-28 Pillar 1 - Topic Profile.Rmd

find_prep <- function(objective){

@@

  if(nrow(data_temp) <= 7) return(NULL)

  #
  # best subset selection
  m <- regsubsets(Grade ~ ., data_temp, nvmax = 6)

  coefi <- coef(m, 6)[-1]  # check that 6 is usually a good subset size

>>>>

find_prep <- function(objective, subset_size = 6){

@@

  if(nrow(data_temp) <= (subset_size + 1)) return(NULL) # perhaps use formula similar to min(8, nrow(df) / 2)

  #
  # best subset selection
  m <- regsubsets(Grade ~ ., data_temp, nvmax = subset_size)

  coefi <- coef(m, subset_size)[-1]  # check that 6 is usually a good subset size
